\section{Resource Management}
\label{sec:resource}

\noindent\textbf{Definition and Purpose:} In order to enable parallel processing, distributed stream frameworks distribute logical workflow plan to physical distribution of work, called \textit{tasks}. Tasks are then distributed to a cluster to ensure parallelism. There are different ways to deploy these logical work plan onto a cluster. 



\noindent \textbf{\\Properties:}

Different stream processing frameworks using various methods to deploy their physical plan, for different purposes. These methods are listed below. 

\begin{itemize}
	
	
	\item \textbf{Round-Robin} One of the most common strategies for stream processing framework to distribute its work is round-robin. Using this strategy, the system iteratively assign the next task in line to the next server in queue. This method ensures that the tasks are distributed evenly across the cluster as well as avoiding tasks assigned to the same jobs being assigned to one server. \Fix{cite}
	
	\item \textbf{Pipeline-oriented}
	Besides round-robinly distributed tasks evenly across the cluster, some stream processing framework uses pipeline-oriented approach while distributing tasks. For these systems, logical plan of the applications are interpreted into physical execution plan. Then physical execution plan are distributed to cluster by its lineage, i.e. all path from data sources to data sinks. All tasks from one lineage is allocate to one worker slot to avoid shuffling traffic.  \Fix{cite}
	
	\item \textbf{First-in-first-out}
	Another approach that is widely adapted by micro-batch stream processing system is FIFO \(First-in-first-out\)) After the logical plan being interpreted to physical execution plan. Jobs are queued and they are assigned to the cluster by the its order in the queue. This method fits micro-batch system in nature.
	

\end{itemize}

\noindent \textbf{\\Solutions, trade-offs and usecases:}

Round-Robin approach, among three methods, ensures even distribution of tasks and load-balancing for each machine in the cluster. However, round-robin approach does not take logical processing plan into account. Pipeline-oriented approach, on the other hand, tries to reduce the shuffle between working instances. However, this approach might cause un-even distribution of work. Finally, FIFO provides a natural solution for scheduling jobs for micro-batching stream processing frameworks. This approach also ensures even distribution of work. 


\noindent \textbf{\\Future Direction:}  
.




